Software Citation Principles

### 2016-08-21 sc-principles/rebuttal-2/rebuttal.tex

However, there are two aspects of the latest version that I find not very
convincing:
}

\begin{enumerate}

\item \textbf{Reviewer comment:}
\emph{The listed differences between software and data (lines 100--114) are not
convincing in my opinion:}

\begin{itemize}
{\itshape

\item ``Software can be used to express or explain concepts, unlike
data'': I don't understand this.

\item ``Software is updated more frequently that papers or data''
(typo: ``that'' instead of ``than''): This was questioned also by the
second reviewer, and I don't think the issue is resolved. The footnote is
unsupported and seems to partly contradict the main point. (I can imagine that
maybe only *popular* software tends to be updated frequently, whereas
*popular* dataset are often not.)

\item ``Software suffers from a different type of bit rot than data'':
I am not convinced that this is really a different *type* of bit rot.
In particular datasets in proprietary formats seem to suffer from exactly the
same problems.

\item ``Software is frequently built to use other software'': True,
though similar things can occur in datasets too, in particular with respect to
Linked Data, where datasets typically use a number of third-party ontologies and
vocabularies.

\item ``Software is generally smaller than data'': Another unsupported
claim, and I am not fully convinced that this is true. There must be a large
number of very small spreadsheets of data. So, on average data might be smaller
than software. The difference is certainly true on the upper end of the scale
though: the largest datasets are larger than the largest pieces of software.

\item ``Software teams can be large and multidisciplinary, \ldots'': I think
this applies to data too.

\item ``The lifetime of software is generally not as long as that of data.'':
Again unsupported, and again I can imagine this to be false. Many datasets, in
particular small ones, might be stillbirths (i.e.\ they are never used). The
same might be true for software, but possibly to a lesser degree. And software
might commonly evolve, whereas data might more often be replaced by a
different and newer dataset, in which case evolving software would live
longer.
}

### 2016-08-27 sc-principles/software-citation-principles.tex
turning line numbers off
removing extra outline at the end of section 3

% add line numbers for submission
\usepackage{lineno}
\linenumbers

@@

The main contribution of this document are the software citation principles,
written fairly concisely in this section and discussed further later in the
document (\S\ref{sec:discussion}). In addition, we also motivate the creation
of these principles (\S\ref{sec:intro}), describe the process by which they
were created (\S\ref{sec:process}), summarize use cases related to software
citation (\S\ref{sec:use_cases}), and review related work
(\S\ref{sec:related_work}). We also lay out the necessary future work
(\S\ref{sec:futurework}).
%The principles in this section are written fairly concisely, and discussed
%further later in this document (\S\ref{sec:discussion}). Here, for example,
%we do not define what software should be cited, but how it should be
%cited, and we talk about how such decisions might be made in the
%discussion section~(\S\ref{sec:discussion}).

@@

In the next section~(\S\ref{sec:use_cases}), we provide some detailed context in
which software citation is important, by means of use cases. In
\S\ref{sec:related_work}, we summarize and analyze a large amount of previous
work and thinking in this area. In \S\ref{sec:discussion}, we discuss issues
related to the principles stated in \S\ref{sec:principles}, and finally, in
\S\ref{sec:futurework} we discuss the work needed to lead to these
software citation principles being applied.

>>>>

% add line numbers for submission
\usepackage{lineno}
%\linenumbers

@@

The main contribution of this document are the software citation principles,
written fairly concisely in this section and discussed further later in the
document (\S\ref{sec:discussion}). In addition, we also motivate the creation
of these principles (\S\ref{sec:intro}), describe the process by which they
were created (\S\ref{sec:process}), summarize use cases related to software
citation (\S\ref{sec:use_cases}), and review related work
(\S\ref{sec:related_work}). We also lay out  
the work needed to lead to these
software citation principles being applied (\S\ref{sec:futurework}).
%The principles in this section are written fairly concisely, and discussed
%further later in this document (\S\ref{sec:discussion}). Here, for example,
%we do not define what software should be cited, but how it should be
%cited, and we talk about how such decisions might be made in the
%discussion section~(\S\ref{sec:discussion}).

@@
